### 2018-04-28 paper/algorithm.tex
Adapts algorithm to building blocks
Incorporated Adrien's old stuff further, disposition

We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
\(D_u\).
We call \(D_u\) the device swarm of \(u\).
Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
swarm, \(D_b\).
We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
swarm.

Without loss of generality, we will use Alice and Bob as examples.
Each of Alice's (and Bob's) devices will keep track of its own online and 
offline behaviour.
They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
each other's online--offline behaviour.
\commentDaniel{Is that correct?}
This allows Alice's device swarm to do internal scheduling.

Each device \(d\in D_a\) will also participate in the global device swarm, 
\(D\supset D_a\).

\subsection{Adrien's old stuff}

\newcommand{\localoverlay}{Local Overlay\xspace}
\newcommand{\globaloverlay}{Global Overlay\xspace}

\subsection{The \localoverlay}%
\label{local-overlay}

A user's devices, \(D_i\), use the \localoverlay to:
\begin{enumerate}
	\item Share information about the user's behavior.
	Devices use it to build a behavioral model and infer their future connection probability;
  \item Share files location \commentAL{Maybe \dots}
\end{enumerate}

@@

\subsection{The \globaloverlay}%
\label{global-overlay}

@@

@@

\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\GetRouteNode}{GetRouteNode}
\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}

\NewAlgorithm{\Enc}{Enc}
\NewVariable{\pk}{pk}

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
      \(D\) is a set of device addresses.
      $\pk_D$ is the public key of device set $D$.
      $L$ is the length of the route,
      $\theta$ is the threshold of probability of failure.%
    }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \GetRouteNode[\theta]$
      \State $H\gets D\concat \Enc[_{\pk_{D}}][H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction

    \Function{\GetRouteNode}{$\theta$}
      \State $D\gets \GetRandomPeer$
      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
        \State $D\gets D\cup \GetRandomPeer$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \caption{\label{ExtendRoute}%
    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
    failure threshold of \(\theta\) for each hop in the route.
    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
  }
\end{figure}

@@

    \Function{\Store}{$c_m$}
      \State $m\gets \Dec[_{\sk_D}][c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORRecv}%
    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
    It creates a probabilistic onion-route from a rendez-vous point to its own 
    devices and returns the route to the sender.
    The \(\Store\) algorithm is used by the local \(\SPOR[\Fwd]\) algorithm to 
    store messages intended for itself.
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $m$ is the message to be sent,
      $\pk_D$ is the public-key of the recipient,
      $H_\rdv$ is the onion-route given by the recipient.
    }
    \Function{\SPOR[\Send]}{$m, \pk_D, H_\rdv$}
      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
      \State $c_m\gets \Enc[_{\pk_D}][m]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H, c_m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORSend}%
    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
    recipient.
    \(\pk_D\) is the public key of the recipient.
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$C_H, c_m$}
      \State $H\gets \Dec[_\sk][C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[c_m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', c_m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORFwd}%
    The \(\SPOR[\Fwd]\) algorithm forwards \(c_m\) down the route \(H\), 
    obtained by decrypting \(C_H\) with the node's associated private key.%
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\) (\cref{SPORRecv}).%
  }
\end{figure}

@@

\endinput

% subsubsection onion_routes_in_face_of_churn (end)

% \begin{figure}[t]
% \centering
% \includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
% \caption{\label{fig:pipeline}Pipeline of the steps undergone by Alice when he shares a file from his laptop L with Bob.}
% \end{figure}

% \Cref{fig:pipeline} depicts the process of a file exchange from Alice to Bob.
% The file $f$ is initially located on Alice's laptop $L$, which is potentially offline for now.
% Firstly, Alice and Bob need to exchange encryption keys and the key $ID_f$ 
% referencing the file on the \ac{DHT}.
% They do so \emph{out-of-band}, that is using another channel than the one 
% presented here (\eg bluetooth, email, \etc).

% Then, Alice queries the DHT for devices that will most likely be online at the same time as his laptop $L$.
% To this end, Alice uses his knowledge on his devices connection patterns $A_i$, along with the DHT's public information on devices connections.
% Once Alice and the DHT agreed upon a set of peers $(M_1, M_2, M_3)$, their address is put in the DHT at the key $ID_f$ referencing the file of interest.

% At the third step, Alice's laptop $L$ becomes available. 
% Informed of the ongoing file exchange by Alice's Device Swarm Protocol, $L$ fetches the addresses of $M_1, M_2$ and $M_3$ on the DHT using the key $ID_f$.
% These peers will serve as middle-men: $L$ sends them redundant chunks of $f$ through an onion route (thus remaining anonymous), for Bob to fetch them later.

% In the last forth step, Bob fetches the file $f$ using any of her devices.
% To do so, she uses the key $ID_f$ to learn the addresses of $M_1, M_2$ and $M_3$.
% Then, she fetches parts of $f$ from the online middle-men through an onion route.
% Given that $L$ sent redundant chunks to the middle-men, Bob will not need every middle-man to be connected to fetch the whole file.
% Once Bob has completed the download, the key $ID_f$ is flushed on the DHT.

>>>>

We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
\(D_u\).
We call \(D_u\) the device swarm of \(u\).
Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
swarm, \(D_b\).
We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
swarm.
Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
Bob, with device swarm \(D_b\), as examples.

\subsection{The local swarm}%
\label{local-overlay}

Each of Alice's (and Bob's) devices will keep track of its own online and 
offline behaviour.
They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
each other's online--offline behaviour.
\commentDaniel{Is that correct?}
This allows Alice's device swarm to infer a behavioural model for the device 
swarm and do internal scheduling based on the probability of being online.

@@

@@

\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}

@@

\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\GetRouteNode}{GetRouteNode}

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
      \(D\) is a set of device addresses.
      $\pk_D$ is the public key of device set $D$.
      $L$ is the length of the route,
      $\theta$ is the threshold of probability of failure.%
    }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \GetRouteNode[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction

    \Function{\GetRouteNode}{$\theta$}
      \State $d\gets \GetRandomPeer$
      \State $D\gets \{d\}$
      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
        \State $d\gets \GetRandomPeer$
        \State $D\gets D\cup \{d\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \caption{\label{ExtendRoute}%
    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
    failure threshold of \(\theta\) for each hop in the route.
    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
  }
\end{figure}

@@

    \Function{\Store}{$c_m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORRecv}%
    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
    It creates a probabilistic onion-route from a rendez-vous point to its own 
    devices and returns the route to the sender.
    The \(\Store\) algorithm is used by the local \(\SPOR[\Fwd]\) algorithm to 
    store messages intended for itself.
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $m$ is the message to be sent,
      $\pk_D$ is the public-key of the recipient,
      $H_\rdv$ is the onion-route given by the recipient.
    }
    \Function{\SPOR[\Send]}{$\mpk, D, H_\rdv, m$}
      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
      \State $c_m\gets \DeBEenc[\mpk, D, m]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H, c_m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORSend}%
    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
    recipient.
    \(\pk_D\) is the public key of the recipient.
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$C_H, c_m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[c_m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', c_m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORFwd}%
    The \(\SPOR[\Fwd]\) algorithm forwards \(c_m\) down the route \(H\), 
    obtained by decrypting \(C_H\) with the node's associated private key.%
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\) (\cref{SPORRecv}).%
  }
\end{figure}

@@
